\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}     
\usepackage{latexsym}
\geometry{left=2.5cm,right=2.5cm,top=2.5cm,bottom=2.5cm}
\usepackage{fancyhdr}
\pagestyle{fancy}
\usepackage{amssymb}
\title{CS6003-INET Foundation of Computer Science Problem Set3}
\author{Robert Wen (robert.wen@nyu.edu), NetID: qw476, N12246277}
\date{September 2015}

\begin{document}
\begin{large}

\maketitle


1. Suppose you wish to use the Principle of Mathematical Induction to prove that
1$\cdot$1!+2$\cdot$2!+3$\cdot$3! + $\cdots$ +n$\cdot$n!=(n+1)! - 1 for all n $\ge$ 1.

(a) Write P(1) (b) Write P(5) (c) Write P(k) (d) Write P(k+1) (e) Use the Principle of Mathematical Induction to prove that P(n) is true for all n

(a) P(1) = 1$\cdot$1! = 1

(b) P(5) = 1$\cdot$1! + 2$\cdot$2! + 3$\cdot$3! + 4$\cdot$4! + 5$\cdot$5!
         = 1$\cdot$1  + 2$\cdot$2  + 3$\cdot$6  + 4$\cdot$24 + 5$\cdot$120
         = 719

(c) P(k) = 1$\cdot$1! + 2$\cdot$2! + 3$\cdot$3! + ... + k$\cdot$k!

(d) P(k+1) = 1$\cdot$1! + 2$\cdot$2! + 3$\cdot$3! + ... + k$\cdot$k! + (k+1)$\cdot$(k+1)!

(e) For n = 1, P(1) = 1$\cdot$1! = 1 = (1+1)! - 1 = 2 - 1 = 1
\indent    Suppose when n = k and k $\ge$ 1, P(k) = 1$\cdot$1! + $\cdots$ + k$\cdot$k! = (k+1)! - 1
\indent    We know P(k+1) = P(k) + (k+1)$\cdot$(k+1)! 
\indent \indent           = (k+1)! - 1 + (k+1)$\cdot$(k+1)!
\indent \indent           = (k+1+1)(k+1)! - 1
\indent \indent           = (k+2)! - 1
\indent \indent           = ((k+1)+1)! - 1
\indent    So for all n where n $\ge$ 1, 1$\cdot$1!+2$\cdot$2!+3$\cdot$3! + $\cdots$ +n$\cdot$n!=(n+1)! - 1

\noindent2. Use the Principle of Mathematical Induction to prove that $n^{3}>n^{2}+3$ for all $n\ge 2$. \\

For n = 2, $n^3$ = 8 > $n^{2} + 3$ = 7
Suppose n = k, we have $k^{3} > k^{2} + 3$
When n = k+1, we have $(k+1)^3 = $k^3$ + 3$k^2$ + 3k + 1
So we have $k^{3} + 3$k^2$ + 3k + 1 > k^{2} + 3 + 3$k^2$ + 3k + 1
           $(k+1)^3 > 4$k^2$ + 3k + 4

As 4$k^2$ + 3k + 4 = k^2 + 2k + 1 + 3 + (3k^2 + k)
                   = (k+1)^2 + 3 + (3k^2 + k)
As k $\ge$ 2, (3k^2 + k) $\gt$ 0
So $(k+1)^3$ > 4$k^2$ + 3k + 4 > (k+1)^2 + 3
So we have $(k+1)^3$ > (k+1)^2 + 3
Therefore for all $n\ge 2$, $n^{3}>n^{2}+3$.

3. Use the Principle of Mathematical Induction to prove that 1+3+9+27+ $\cdots$ +3^n=$\frac\{3^(n+1)−1}{2} for all n $\ge$ 0.

For n = 0, left side = 1, right side = $\frac\{3^(0+1)−1}{2} = $\frac{3-1}{2} = 1. The equality meets
For n = 1, left side = 1 + 3 = 4, right side = $\frac\{3^(1+1)−1}{2} = 4. The equality meets.
For n = k, suppose 1+3+ $\cdots$ + 3^k = $\frac\{3^(k+1)-1}{2}
When n = k+1, (1+3+ $\cdots$ + 3^k) + 3^(k+1) = $\frac\{3^(k+1)-1}{2} + 3^(k+1)
            = $\frac{3^(k+1)-1+2*3^(k+1)}{2}
            = $\frac{3*3^(k+1)-1}{2}
            = $\frac{3^((k+1)+1)-1}{2}
So for all n where n $\ge$ 0, 1+3+9+27+ $\cdots$ +3^n=$\frac\{3^(n+1)−1}{2}.

4. Use the Principle of Mathematical Induction to prove that any integer amount of postage from 18 cents on up can be made from an infinite supply of 4-cent and 7-cent stamps.

Let us remodel the problem as for any n where n $\ge$ 18, there exists a, b $\in$ N, n = 4a + 7b

For n = 18, n = 18 = 4*1 + 7*2, where a = 1, b = 2
For n = 19, n = 19 = 4*3 + 7*1, where a = 3, b = 1
For n = 20, n = 20 = 4*5, where a = 5, b = 0
For n = 21, n = 21 = 7*3, where a = 0, b = 3

Suppose for n = k, we have k = 4a + 7b
Then k + 1 = 4a + 7b + 1
When b $\ge$ 1, k + 1 = 4a + 7(b-1) + 8 = 4(a+2) + 7(b-1)
When b = 0, to let 4a + 7b $\ge$ 18, a must be at least 5 because when a = 4 and b = 0, n = 16 which is less than 18.
So when b = 0, k + 1 = 4a + 1 = 4(a - 5) + 21 = 4(a-5) + 7*3 where a \$ge$ 5

So when n = k + 1, we can find a, b to let n = 4a + 7b

Therefore for any n $\ge$ 18, there exists a, b $\in$ N, n = 4a + 7b.

\noindent5. Prove that $\sum\limits_{j=n}^{2n-1}(2j+1)=3n^{2}$ for all positive integers \emph{n}.\\

For n = 1, left side = $\sum\limits_{j=n}^{2n-1}(2j+1) = 2 * 1 + 1 = 3
           right side = 3*1^2 = 3
For n = 2, left side = $\sum\limits_{j=n}^{2n-1}(2j+1) = 4 + 1 + 6 + 1 = 12
           right side = 3*2^2 = 12
Suppose for n = k, $\sum\limits_{j=k}^{2k-1}(2j+1)=3k^{2}$
for n = k+1, we have $\sum\limits_{j=k+1}^{2k+1}(2j+1)$
                    =$\sum\limits_{j=k}^{2k-1}(2j+1)$ - (2k+1) + (2(2k)+1) + (2(2k+1)+1)
                    =$3k^2 - 2k - 1 + 4k + 1 + 4k + 2 + 1$
                    =$3k^2 + 6k + 3$
                    =$3(k^2 + 2k + 1)$
                    =$3(k+1)^2$
Therefore, for all positive integers \emph{n}, $\sum\limits_{j=n}^{2n-1}(2j+1)=3n^{2}$

6. Use mathematical induction to show that n lines in the plane passing through the same point divide the plane into 2n regions.

For n = 1, obviously the plane will be divided into 2n = 2 regions. So P(1) satisfies.

Suppose for n = k, n lines in the plane passing through the same point divide the plane into 2k regions,

For n = k + 1, we can see the last line as the extra line added to the k lines on the plane scenario. 
That is, there are 2k regions before adding the last line.

As all lines are passing through the same point, we can see the last line must be between two existing lines and divide the existing two regions made by the two lines with 2 extra regions.

That is to say, for n = k + 1, P(k+1) = P(k) + 2 = 2k + 2 = 2(k+1)

Therefore, P(k+1) satisifies when P(k) satisfies.

Therefore, for n lines in the plane passing through the same point divide the plane into 2n regions.

7. Let a$_{1}$=2,a$_{2}$=9, and a$_{n}=2a$_{n−1}+3a$_{n−2} for n $\ge$ 3. Show that an $\le$ 3n for all positive integers n. 

For n = 1, a$_{1}$ = 2 $\le$ 3$^{1}$ = 3
For n = 2, a$_{2}$ = 9 $\le$ 3$^{2}$ = 9
For n = 3, a$_{3}$ = 2a$_{n−1} + 3a$_{n−2} 
                   = 2a$_{2} + 3a$_{1}
                   = 18 + 9
                   = 27 $\le$ 3^3

Suppose for n = k, we have a$_{k}$=2a$_{k−1}+3a$_{k−2}$ $\le$ $3^k$
So we have a$_{k+1} = 2a$_{k}$+3a$_{k−1}$ 
                    = 2a$_{k}$ + $2a_{k−1} + 3a_{k−2}$ + $a_{k−1}$ - $3a_{k-2}$
                    = 2a$_{k}$ + a$_{k} + $a_{k−1}$ - $3a_{k-2}$
So we have a$_{k+1} $\le$ $3^k$ + 2a$_{k}$ + $a_{k−1}$ - $3a_{k-2}$
                    $\le$ $3^k$ + 2$\cdot 3^k$ + $a_{k−1}$ - $3a_{k-2}$ as a$_{k}$ $\le$ $3^k$
So we have a$_{k+1} $\le$ $3^(k+1)$ + $a_{k−1}$ - $3a_{k-2}$

As $a_{k-1}$ - 3$a_{k-2}$ = 2$a_{k-2}$ + 3$a_{k-3}$ - 3$a_{k-2}$
                          = 3$a_{k-3}$ - $a_{k-2}$
                          
???

8. Find the error in the following proof of this “theorem”: “Theorem: Every positive integer equals the next largest positive integer.” “Proof: Let P(n) be the proposition ‘n=n+1’. To show that P(k)→P(k+1), assume that P(k) is true for some k, so that k=k+1. Add 1 to both sides of this equation to obtain k+1=k+2, which is P(k+1). Therefore P(k)→P(k+1) is true. Hence P(n) is true for all positive integers n.”

Before assuming P(k) is true for some k, so that k=k+1, we should show that for specific starting examples stand first.
For example, for n = 1, left side = 1, right side = 1 + 1
Obviously 1 $\neq$ 2
So we cannot assume that P(k) is true for some k because we even cannot find a specific example to let P(k) is true.
Therefore this proof is wrong.

9. Give a recursive definition with initial conditions for the function f(n)=5n+2,n=1,2,3,....

By observation, 
f(1) = 7
f(2) = 12
f(3) = 17
f(4) = 22

Let us assume f(n) = f(n-1) + 5 for $n \ge 2$

For n = 2, we have f(2) = f(1) + 5 = 7 + 5 = 5*2 + 2 = 12, which satisfy P(n)
Let us assume for n = k, we have f(k) = f(k-1) + 5
So for n = k+1, f(k+1) = 5(k+1) + 2 = 5k + 2 + 5
As f(k) = 5k+2
So we have f(k+1) = f(k) + 5

Therefore, the recursive definition of the function f(n) is
f(n) = 7 for $n = 1$
f(n) = f(n-1) + 5 for $n \ge 2$

10. Give a recursive definition with initial conditions for {an} where an=21/2n.

11. Consider the following program segment:

i := 1
total := 1 
while i < n
  i := i + 1
  total := total + i
Let p be the proposition “total =i(i+1)2 and i≤n.” Use mathematical induction to prove that p is a loop invariant.

\end{large}

\end{document}

